Comparing Power Optimizations in the Reorder Buffer

### 2011-06-10 paper/end.tex
Dist ROB section in paper done.

>>>>

\subsection{Distributed ROB}

Our results for the distributed ROB are largely invalid for two reasons. One, much of the savings in the distributed ROB comes from shorter bit-lines and less copmlex entry selection from the size reduction of each individual buffer, however this is not currently modeled in our reorder-buffer simulator. Next, our implementation is actually buggy, as is obvious from the results.

From the first instruction stream, heavy on floating point instructions, we see the distributed buffer measures some thiry thousand less cycles to complete than the circular buffer. In \cite{kucuk4}, the improvement for FP instructions over the base buffer did improve very slightly (we note that they were also modelling a processor with many more FP functional units than the ones we used), but to the degree we see is impossible. We monitored the buffer and indeed found corruption in the contents within the first 30 instructions, but ultimately were unable to find the source of the error.

For all instruction streams, we note that while the circular ROB powered 17,936 bits pe cycle (bit-cycles / cycles), the distributed ROB powered 27,692 bits per cycle. This is largely due to the presence of the central FIFO queue, which must keep a set of pointers to the location of actual entries in the ROB components of each functional unit. The extra cost of this is offset by shorter bit-lines and word-select lines, which as previously mentioned are not currently tabulated.
